### 2015-05-14 background.tex
improvements in bg

The most common technique for eliminating races is using a \emph{locking} mechanism. Locking a set of program statements that access a shared resource with a lock $l$ creates a \emph{critical section}, i.e.\ source code that cannot execute concurrently by threads that hold $l$. Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the data race in Figure~\ref{fig:data_race_example}. The example is tricky, because the return statement can potentially race on the \texttt{f\_pos} field. To fix this issue, we store the result in a temporary variable, inside the critical section.

>>>>

The most common technique for eliminating races is using a lock $l$. Locking a set of program statements that access a shared resource with $l$ creates a \emph{critical section}, i.e.\ source code that can only execute by the thread that holds $l$. Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the data race in Figure~\ref{fig:data_race_example}. The example is tricky, because the return statement can potentially race on the \texttt{f\_pos} field. To fix this issue, we store the result in a temporary variable, inside the critical section.
